An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-05-01 VLDB2026/main.tex
modify

	\textcolor{blue}{Based on the} query performance trends of different algorithms under varying AS \textcolor{blue}{settings}, we categorize the algorithms into 3 groups:

@@

	ACORN-1 performs well in low AS \textcolor{blue}{settings} because fewer nodes share the same attribute. This increases the average degree of retained nodes and improves graph connectivity. CAPS efficiently skips irrelevant subpartitions, reducing computational overhead. However, as AS increases, it must process more subpartitions and handle a larger dataset. StitchedVamana optimizes local adjacency using independent subgraphs, enabling fast localization at low AS. However, at higher AS \textcolor{blue}{settings}, it requires broader global exploration. UNG, Faiss, and Puck all use pre-filtering strategies to shrink the search space in low AS \textcolor{blue}{settings}, leading to better performance.

>>>>

	\textcolor{blue}{Based on the} query performance trends of different algorithms under varying AS, we categorize the algorithms into 3 groups:

@@

	ACORN-1 performs well in low AS because fewer nodes share the same attribute. This increases the average degree of retained nodes and improves graph connectivity. CAPS efficiently skips irrelevant subpartitions, reducing computational overhead. However, as AS increases, it must process more subpartitions and handle a larger dataset. StitchedVamana optimizes local adjacency using independent subgraphs, enabling fast localization at low AS. However, at higher AS, it requires broader global exploration. UNG, Faiss, and Puck all use pre-filtering strategies to shrink the search space in low AS, leading to better performance.
